---
title: "CRISIS- Self Report"
output: 
  html_document:
    self_contained: false
tables: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("dplyr")
library("stringr")
library("reshape2")
library("ggplot2")
library("ggthemes")
library("modelsummary")
library("textclean")
library("ggpubr")
library("Rmisc")
library("sjPlot")
library("gridExtra")
library("kableExtra")
library("readxl")

#Due to privacy reasons these files have not been released. 
#The ones in github don't have PII information, therefore only year is included for dates
dataDirectory="./data/"
s_pre_during_mfq_df=read.csv(paste0(dataDirectory,"s_pre_during_mfq_df.csv"))
s_pre_during_mfq_df=read.csv(paste0(dataDirectory,"s_pre_during_mfq_df.csv"))
p_pre_during_mfq_df=read.csv(paste0(dataDirectory,"p_pre_during_mfq_df.csv"))
s_pre_during_scared_df=read.csv(paste0(dataDirectory,"s_pre_during_scared_df.csv"))
p_pre_during_scared_df=read.csv(paste0(dataDirectory,"p_pre_during_scared_df.csv"))

date1=spring2019=as.Date("2019-03-11")
spring2020=covidTime=as.Date("2020-03-11")
analysisEndDate=as.Date("2021-03-11") 

measureLabels=c("Depressive Symptoms", "Anxiety Symptoms")
measureLabelsForPlots=c("Depressive Score (self report)","Anxiety Score (self report)")
ylims=c(30, 30, 12, 12)
baseFontSize=14

source("./source/prepareDataset.R", local = knitr::knit_global())
source("./source/prepareBehavioralDataSet.R", local = knitr::knit_global())

ct1=read.csv(paste0(dataDirectory,"s_pandemic_mfq_and_crisis_df.csv")) #this is the same for scared
behavioralData=prepareBehavioralDataSet(ct1)

s_mfq=prepareDataSet(s_pre_during_mfq_df,"s_mfq")
s_mfq = s_mfq %>% filter(s_mfq_tot < 27)
s_scared=prepareDataSet(s_pre_during_scared_df,"s_scaredshort")

s_mfq$Year=factor(s_mfq$Year, levels=c("2019","2020"),labels=c("Pre-Pandemic","Pandemic")) #this takes March into account, it's March 2019-2020 and 2020-2021. For more details look at prepareDateset.R
s_scared$Year=factor(s_scared$Year, levels=c("2019","2020"),labels=c("Pre-Pandemic","Pandemic")) #this takes March into account

#************** excluding subjects that had inpatient/outpatient visits ---------------------------------
s_mfq_with_inout=s_mfq %>% filter(as.Date(measureDate) >= spring2019 & as.Date(measureDate) < analysisEndDate) %>% filter(grepl("^o", Clinical_Visit_Type) | grepl("^i", Clinical_Visit_Type))
s_mfq_with_no_in_out=s_mfq %>% filter(!Participant %in% s_mfq_with_inout$Participant) #134
s_mfq_with_in_out=s_mfq %>% filter(Participant %in% s_mfq_with_inout$Participant) #32

s_scared_with_inout=s_scared %>% filter(as.Date(measureDate) >= spring2019 & as.Date(measureDate) < analysisEndDate) %>% filter(grepl("^o", Clinical_Visit_Type) | grepl("^i", Clinical_Visit_Type))
s_scared_with_no_in_out=s_scared %>% filter(!Participant %in% s_scared_with_inout$Participant) #134


#************** Make subgroups based on whether it's a ongoing MDD or not ------------------------------
s_mfq$Clinical_Visit_Date=as.Date(s_mfq$Clinical_Visit_Date)
lastVisitBeforeCovid=s_mfq %>% select(Participant, c_ksadsdx_primary_dx,c_ksadsdx_dx_detailed,Group, s_mfq_tot, s_mfq_date, Clinical_Visit_Date) %>% 
  filter(!is.na(Clinical_Visit_Date) & Clinical_Visit_Date< covidTime)%>% arrange(Clinical_Visit_Date) %>% group_by(Participant) %>% slice(n())
MDDgroup=lastVisitBeforeCovid %>% filter(Group=="MDD")

history=MDDgroup %>% filter(c_ksadsdx_dx_detailed=="Hist_MDD" | c_ksadsdx_dx_detailed=="Sub_hist" | c_ksadsdx_dx_detailed=="Hist_Sub") #23
history$Participant=droplevels(history$Participant)
ongoing=MDDgroup %>% filter(c_ksadsdx_dx_detailed=="Full_MDD")
ongoing$Participant=droplevels(ongoing$Participant)


```

### Question 1:  Has the COVID-19 pandemic impacted adolescent depression and anxiety symptoms?
### Depressive Symptoms
#### Q1- MFQ: Average depressive symptoms before and during the pandemic.
```{r mfq-q1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE} 

q1lmeHVMDD=lmerTest::lmer(measureName~Gender+Year*Group+(1+Year|Participant), data=s_mfq, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
#summary(q1lmeHVMDD)
tab_model(q1lmeHVMDD,dv.labels =c("Depressive Symptoms"))
#differnet contrasts
a=lmerTest::contest1D(q1lmeHVMDD, c(1,0,0,1,0),confint=TRUE) #to get just MDD before pandemic
b=lmerTest::contest1D(q1lmeHVMDD, c(1,0,1,1,1),confint=TRUE) #to get just MDD after pandemic
c=lmerTest::contest1D(q1lmeHVMDD, c(1,0,0,0,0),confint=TRUE) #HV before
d=lmerTest::contest1D(q1lmeHVMDD, c(1,0,1,0,0),confint=TRUE) #HV after

#effect size
s_mfq_hv_before=s_mfq %>% filter(Year=="Pre-Pandemic" & Group=="HV")
s_mfq_hv_after=s_mfq %>% filter(Year=="Pandemic" & Group=="HV")
s_mfq_hv_before1=s_mfq_hv_before %>% group_by(Participant) %>% dplyr::summarize(avg=mean(s_mfq_tot))
s_mfq_hv_after1=s_mfq_hv_after %>% group_by(Participant) %>% dplyr::summarize(avg=mean(s_mfq_tot))
hvCohenD=(mean(s_mfq_hv_after1$avg)-mean(s_mfq_hv_before1$avg))/(sd(s_mfq_hv_after1$avg-s_mfq_hv_before1$avg))
print("-------- Cohen's d for HV -----------")
print(hvCohenD,digits=3)

s_mfq_mdd_before=s_mfq %>% filter(Year=="Pre-Pandemic" & Group=="MDD")
s_mfq_mdd_after=s_mfq %>% filter(Year=="Pandemic" & Group=="MDD")
s_mfq_mdd_before1=s_mfq_mdd_before %>% group_by(Participant) %>% dplyr::summarize(avg=mean(s_mfq_tot))
s_mfq_mdd_after1=s_mfq_mdd_after %>% group_by(Participant) %>% dplyr::summarize(avg=mean(s_mfq_tot))
mddCohenD=(mean(s_mfq_mdd_after1$avg)-mean(s_mfq_mdd_before1$avg))/(sd(s_mfq_mdd_after1$avg-s_mfq_mdd_before1$avg))
print("-------- Cohen's d for participants with MDD -----------")
print(mddCohenD,digits=3)

#type=int - interactions based on conditional mean, pred: based on conditional mean (conditioned on reference levels of factors), eff: based on marginal means (marginalized/averaged over the levels of factors)
#Average of depressive symptoms before and during the pandemic
mfqp1=sjPlot::plot_model(q1lmeHVMDD, show.intercept = TRUE, title="", type="pred",terms=c("Year","Group","Gender"),dodge = .2,axis.labels = "", legend.title = "")+ylim(c(-2,16))+theme_classic(base_size=baseFontSize)+ylab("Depressive Symptoms")+xlab(" ")+theme(axis.text.x=element_text(hjust=c(.3,.6)))
mfqp1

ggeffects::ggemmeans(q1lmeHVMDD, terms=c("Year", "Group","Gender"))

```


#### Q1-MFQ - part b: Trajectory of depressive symptoms before and during the pandemic for MDD participants. 
```{r mfq-q2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE} 

smqf2020N=s_mfq%>%group_by(Participant, Year) %>% dplyr::count(.)
ParticipantLessThan2=smqf2020N %>% filter(n < 2)
smfqTraj=s_mfq%>%filter(Group=="MDD" & !(Participant %in% ParticipantLessThan2$Participant))#59

mfqq2lme=lmerTest::lmer(measureName~Gender+Time*Year+(1+Time*Year|Participant), data=smfqTraj, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

sjPlot::tab_model(mfqq2lme,dv.labels= "Depressive Symptoms")
a=lmerTest::contest1D(mfqq2lme, c(0,0,1,0,1),confint=TRUE) #to get just MDD
print("Slope of the trajectory during the pandemic (Time + Time * Year [Pandemic]")
print(a, digits=3)

mfqp2=sjPlot::plot_model(mfqq2lme, show.intercept = TRUE, title="", type="pred",terms=c("Time","Year","Gender"),colors=c("darkgreen","purple"), legend.title="") 
mfqp2=mfqp2+ylab("Depressive Symptoms")+xlim(c(0,12))+ylim(c(-2,18))+scale_x_discrete(name ="", 
                    limits=c("April","May","June","July","August","September","October","November","December","January","February"))
mfqp2=mfqp2+ theme_classic(base_size=16) + theme(axis.text.x = element_text(angle=90))
mfqp2


```

### Anxiety Symptoms - Anxiety Symptoms
####Q1- SCARED: Average anxiety symptoms before and during the pandemic.
##### HV and MDD together
```{r scared-q1, eval=TRUE, echo=FALSE, warning=FALSE} 
scaredq1lmeHVMDD=lmerTest::lmer(measureName~Gender+Year*Group+(1+Year|Participant), data=s_scared, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
#summary(scaredq1lmeHVMDD)
a=lmerTest::contest1D(scaredq1lmeHVMDD, c(1,0,0,0,0),confint=TRUE) #HV before
b=lmerTest::contest1D(scaredq1lmeHVMDD, c(1,0,1,0,0),confint=TRUE) #HV after
c=lmerTest::contest1D(scaredq1lmeHVMDD, c(1,0,0,1,0),confint=TRUE) #to get just MDD
d=lmerTest::contest1D(scaredq1lmeHVMDD, c(1,0,1,1,0),confint=TRUE) #to get just MDD

sjPlot::tab_model(scaredq1lmeHVMDD,dv.labels= "Anxiety Symptoms")

scaredp1=sjPlot::plot_model(scaredq1lmeHVMDD, show.intercept = TRUE, title="",legend.title = "",dodge = .2, type="pred",terms=c("Year","Group","Gender"))+ylim(c(-.5,4.5))+theme_classic(base_size=baseFontSize)+ylab("Anxiety Symptoms")+xlab(" ") +theme(axis.text.x=element_text(hjust=c(.3,.6)))
scaredp1

ggeffects::ggemmeans(q1lmeHVMDD, terms=c("Year", "Group","Gender"))

```

#### Q1-SCARED part b: Trajectory of anxiety symptoms before and during the pandemic for MDD participants. 
```{r scared-q2, eval=TRUE, echo=FALSE, warning=FALSE} 

sscared2020N=s_scared%>%group_by(Participant, Year) %>% dplyr::count(.)
ParticipantLessThan2=sscared2020N %>% filter(n < 2)
sscaredTraj=s_scared%>%filter(Group=="MDD" & !(Participant %in% ParticipantLessThan2$Participant))

a=sscaredTraj %>% group_by(Participant) %>% slice(1)

scaredq2lme=lmerTest::lmer(measureName~Gender+Time*Year+(1+Time*Year|Participant), data=sscaredTraj,control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
#summary(scaredq2lme)
sjPlot::tab_model(scaredq2lme,dv.labels= "Anxiety Symptoms")
a=lmerTest::contest1D(scaredq2lme, c(0,0,1,0,1),confint=TRUE) #to get slope during pandemic
print("Slope during the pandemic (Time + Time * Year [Pandemic])")
print(a, digits=3)

scaredp2=plot_model(scaredq2lme, title="", type="pred", terms=c("Time","Year", "Gender"),colors=c("darkgreen","purple"), legend.title="")+ylab("Anxiety Symptoms")+xlim(c(0,12.5))+ylim(c(-.5,4.5))+scale_x_discrete(name ="", 
                    limits=c("April","May","June","July","August","September","October","November","December","January","February"))
scaredp2=scaredp2+ theme_classic(base_size=16) + theme(axis.text.x = element_text(angle=90))
scaredp2

```


#### Q1- Average MFQ and SCARED for HV and MDD: Comparision of depression and anxiety symptoms between healthy and depressed participants.
```{r mfq-scared-q1, eval=TRUE, echo=FALSE, warning=FALSE} 
tab_model(q1lmeHVMDD,scaredq1lmeHVMDD, dv.labels =c("Depressive Symptoms","Anxiety Symptoms"),show.re.var = FALSE, string.pred=" ", file="self-mfq-scared-q1part1-female-male.html")

```

#### Q1- Trajecotry of MFQ and SCARED for MDD: Comparision of depression and anxiety symptoms of depressed participants before and during the pandemic.
```{r mfq-scared-q2, eval=TRUE, echo=FALSE, warning=FALSE} 
tab_model(mfqq2lme,scaredq2lme, dv.labels =c("Depressive Symptoms","Anxiety Symptoms"),show.re.var = FALSE, string.pred=" ", file="self-mfq-scared-q1part2-female-male.html")

```

### Question 2: How have behaviors and worries changed over time during the pandemic?
```{r q2, eval=TRUE, echo=FALSE, warning=FALSE}

behavioralDataN=behavioralData%>%group_by(Participant) %>% dplyr::count(.)
ParticipantLessThan2=behavioralDataN %>% filter(n < 2)

behavioralData2=behavioralData %>% filter(!Participant %in% ParticipantLessThan2$Participant)
behavioralData2n=behavioralData2 %>% group_by(Participant,Group) %>% dplyr::count()
behavioralData2nHV= behavioralData2n%>%filter(Group=="HV")
behavioralData2nMDD=behavioralData2n%>%filter(Group=="MDD")

behavioralData2nSummary=rbind(summary(behavioralData2nHV$n),summary(behavioralData2nMDD$n))
rownames(behavioralData2nSummary)=c("HV","MDD")

models <- list()
sleepmodels=list()
#Lme with waves as continuse var - number of months since pandemic to match the rest of lmes
varnames=c("s_mfq_tot","s_scared_combined_tot","s_worry_total", "s_crisis_28_sleep1", "s_crisis_28_sleep2", "s_crisis_29_exercise", "s_crisis_30_outdoors", "s_crisis_19_relationships_family", "s_crisis_21_relationships_friends","s_crisis_43_video_games", "s_crisis_42_soc_media","s_crisis_41_tv")
labels=c("MFQ","SCARED","Worry", "Sleep < 6", "Sleep > 10", "Exercise", "Time Spent Outdoors", "Family Relationship", "Friends Relationship","Time Spent Playing Video Games", "Social Media","TV")

#since already done mfq/scared above
for(i in 3:length(varnames)){

  y=varnames[i]
  modellabel=labels[i]
  someData2=behavioralData %>% filter(!Participant %in% ParticipantLessThan2$Participant) %>% select(Participant, Gender, Group, s_crisis_date,y=varnames[i])
  someData2$s_crisis_date=as.Date(someData2$s_crisis_date)
  someData2$Time=as.numeric(someData2$s_crisis_date - covidTime)/30.5

  someData2 = someData2 %>% filter(!is.na(y) & !is.na(Time) & !is.na(Gender) & !is.na(Group))

  someData2$y=as.numeric(someData2$y)
  someData2$Gender=toupper(someData2$Gender)
  someData2$Gender=as.factor(someData2$Gender)
  someData2$Participant=as.factor(someData2$Participant)
  divider="####### LME with Wave Summary ##############"

  if(y=="s_crisis_28_sleep1" | y=="s_crisis_28_sleep2"){

      lmeWave=lme4::glmer(y~Gender+Group*Time+ (1|Participant), family="binomial", data=someData2, control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
      sleepmodels[[modellabel]]=lmeWave #skipping sleep here as the interpretation of model parameters would be different

  }else{

    lmeWave=lmerTest::lmer(y~Gender+Group*Time+ (1+Time|Participant), data=someData2, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
    models[[modellabel]]=lmeWave

  }

}

#the ones with p values less than .005 (0.05 bonferroni corrected -> 0.005) are considered significant in the paper
tab_model(models$Worry, models$`Family Relationship`,show.re.var=FALSE,string.pred=" ",dv.labels=c("Worry", "Family Relationship"), file="self-worry-family-2time-points.html")
tab_model(models$`Time Spent Playing Video Games`, models$TV, models$`Social Media`,show.re.var=FALSE,string.pred=" ",dv.labels =c("Time spent playing video Games","Time Spent watching TV","Time spent on social media"), file="self-tv-media-2time-points.html")

#supplemental Table
tab_model(models$`Friends Relationship`,models$Exercise, models$`Time Spent Outdoors`,sleepmodels$`Sleep < 6`, sleepmodels$`Sleep > 10`, show.re.var=FALSE,string.pred=" ",dv.labels=c("Friend Relationship","Exercise","Time Spent outdoors","Sleep < 6 hours", "Sleep > 10 hours"),file="self-behavior-supplemental-table.html")

```

### Sensitivity analysis
##### HV vs. MDD current vs. MDD past
```{r mfq-s4, eval=TRUE, echo=FALSE, warning=FALSE} 

s_mfq_mdd=s_mfq %>% filter(Group=="MDD")
s_mfq_mdd=s_mfq_mdd %>% mutate(Group=ifelse(Participant %in% ongoing$Participant,"ongoingMDD","RestOfMDD"))
s_mfq_hv_mdd3=rbind(s_mfq_mdd,s_mfq %>% filter(Group=="HV"))
s_mfq_hv_mdd3$Group=as.factor(s_mfq_hv_mdd3$Group)  
numbers=s_mfq_hv_mdd3 %>% dplyr::count(Group, Participant)

q1lmeMDD3=lmerTest::lmer(measureName~Gender+Year*Group+(1+Year|Participant), data=s_mfq_hv_mdd3, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#scared
s_scared_mdd=s_scared %>% filter(Group=="MDD")
s_scared_mdd=s_scared_mdd %>% mutate(Group=ifelse(Participant %in% ongoing$Participant,"ongoingMDD","RestOfMDD"))
s_scared_hv_mdd3=rbind(s_scared_mdd,s_scared %>% filter(Group=="HV"))
s_scared_hv_mdd3$Group=as.factor(s_scared_hv_mdd3$Group)
numbers=s_scared_hv_mdd3 %>% dplyr::count(Group, Participant)

q1lmeMDD3Scared=lmerTest::lmer(measureName~Gender+Year*Group+(1+Year|Participant), data=s_scared_hv_mdd3, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

tab_model(q1lmeMDD3,q1lmeMDD3Scared, dv.labels =c("Depressive Symptoms","Anxiety Symptoms"),show.re.var = FALSE, string.pred=" ", file="sensitivityAnalysis-mfq-scared-current-past-MDD-and-HV.html")

g1=lmerTest::contest1D(q1lmeMDD3, c(0,0,0,0,0,1,-1),confint=TRUE)
print("----Contrast for comparing Ongoing MDD vs. Rest of MDD interaction terms for Depressive Symptoms ")
print(g1,digits=3)

g2=lmerTest::contest1D(q1lmeMDD3Scared, c(0,0,0,0,0,1,-1),confint=TRUE)
print("----Contrast for comparing Ongoing MDD vs. Rest of MDD interaction terms for Anxiety Symptoms ")
print(g2,digits=3)

```


### CBT
#how many CBT before and during COVID
```{r mfq-cbt, eval=TRUE, echo=FALSE, warning=FALSE} 

outduring=s_mfq %>% filter(as.Date(measureDate) >= covidTime & as.Date(measureDate) < analysisEndDate) %>% filter(grepl("^o", Clinical_Visit_Type))
induring=s_mfq %>% filter(as.Date(measureDate) >= covidTime & as.Date(measureDate) < analysisEndDate) %>% filter(grepl("^i", Clinical_Visit_Type))

outpre=s_mfq %>% filter(as.Date(measureDate) >= spring2019 & as.Date(measureDate) < covidTime) %>% filter(grepl("^o", Clinical_Visit_Type))
inpre=s_mfq %>% filter(as.Date(measureDate) >= spring2019 & as.Date(measureDate) < covidTime) %>% filter(grepl("^i", Clinical_Visit_Type))

cbtpre=union(outpre$Participant,inpre$Participant)
cbtpost=union(outduring$Participant,induring$Participant)
op=union(outpre$Participant,outduring$Participant)
ip=union(inpre$Participant,induring$Participant)

cbt=matrix(NA, nrow=2,ncol=2)
colnames(cbt)=c("before pandemic","continued or started after the pandemic")
rownames(cbt)=c("inpatient","CBT")
cbt[1,]=c(length(unique(inpre$Participant)),length(unique(induring$Participant))) #1 common in inpre/induring
cbt[2,]=c(length(unique(outpre$Participant)),length(unique(outduring$Participant))) #2 common in outpre/outduring
p=kable(cbt,format = "html", full_width = T,font_size = 12,position = "left")

print(paste("Total number of participants that participated in CBT during March 2019-March 2021 - some participated in both inpatient and outpatient: ",length(union(ip,op))))
print(paste("Total number of participants that participated in CBT prior to the start of the pandemic:",length(cbtpre)))
print(paste("Total number of participants that continued CBT or started CBT after the pandemic:",length(cbtpost)))

```


#### Sensitivity Analysis- Comparision of depression and anxiety symptoms between healthy and depressed participants excluding subjects with inpatient/outpatient treatment.
```{r mfq-q1b, eval=TRUE, echo=FALSE, warning=FALSE} 

q1lmeHVMDDsen=lmerTest::lmer(measureName~Gender+Year*Group+(1+Year|Participant), data=s_mfq_with_no_in_out, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))


#effect size
s_mfq_hv_before=s_mfq_with_no_in_out %>% filter(Year=="Pre-Pandemic" & Group=="HV")
s_mfq_hv_after=s_mfq_with_no_in_out %>% filter(Year=="Pandemic" & Group=="HV")
s_mfq_hv_before1=s_mfq_hv_before %>% group_by(Participant) %>% dplyr::summarize(avg=mean(s_mfq_tot))
s_mfq_hv_after1=s_mfq_hv_after %>% group_by(Participant) %>% dplyr::summarize(avg=mean(s_mfq_tot))
hvCohensD=(mean(s_mfq_hv_after1$avg)-mean(s_mfq_hv_before1$avg))/(sd(s_mfq_hv_after1$avg-s_mfq_hv_before1$avg))

s_mfq_mdd_before=s_mfq_with_no_in_out %>% filter(Year=="Pre-Pandemic" & Group=="MDD")
s_mfq_mdd_after=s_mfq_with_no_in_out %>% filter(Year=="Pandemic" & Group=="MDD")
s_mfq_mdd_before1=s_mfq_mdd_before %>% group_by(Participant) %>% dplyr::summarize(avg=mean(s_mfq_tot))
s_mfq_mdd_after1=s_mfq_mdd_after %>% group_by(Participant) %>% dplyr::summarize(avg=mean(s_mfq_tot))
mddCohenD=(mean(s_mfq_mdd_after1$avg)-mean(s_mfq_mdd_before1$avg))/(sd(s_mfq_mdd_after1$avg-s_mfq_mdd_before1$avg))

#differnet contrasts
a=lmerTest::contest1D(q1lmeHVMDDsen, c(1,0,0,1,0),confint=TRUE) #to get just MDD before pandemic
b=lmerTest::contest1D(q1lmeHVMDDsen, c(1,0,1,1,1),confint=TRUE) #to get just MDD after pandemic
c=lmerTest::contest1D(q1lmeHVMDDsen, c(1,0,0,0,0),confint=TRUE)
d=lmerTest::contest1D(q1lmeHVMDDsen, c(1,0,1,0,0),confint=TRUE)

e=lmerTest::contest1D(q1lmeHVMDDsen, c(0,0,1,0,1),confint=TRUE) #MDD after - MDD before

scaredq1lmeHVMDDsen=lmerTest::lmer(measureName~Gender+Year*Group+(1+Year|Participant), data=s_scared_with_no_in_out, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
#summary(scaredq1lmeHVMDDsen)
#tab_model(scaredq1lmeHVMDDsen,dv.labels =c("Anxiety Symptoms"))
a=lmerTest::contest1D(scaredq1lmeHVMDDsen, c(1,0,0,0,0),confint=TRUE) #HV before
b=lmerTest::contest1D(scaredq1lmeHVMDDsen, c(1,0,1,0,0),confint=TRUE) #HV after
c=lmerTest::contest1D(scaredq1lmeHVMDDsen, c(1,0,0,1,0),confint=TRUE) #to get just MDD
d=lmerTest::contest1D(scaredq1lmeHVMDDsen, c(1,0,1,1,0),confint=TRUE) #to get just MDD

tab_model(q1lmeHVMDDsen,scaredq1lmeHVMDDsen, dv.labels =c("Depressive Symptoms","Anxiety Symptoms"),show.re.var = FALSE, string.pred=" ", file="sensitivity-analysis-self-hv-mdd-mfq-scared-q1part1-female-male.html")

mfqp1=sjPlot::plot_model(q1lmeHVMDDsen, show.intercept = TRUE, title="", type="pred",terms=c("Year","Group","Gender"),dodge = .2,axis.labels = "", legend.title = "")+ylim(c(-2,16))+theme_classic(base_size=baseFontSize)+ylab("Depressive Symptoms")+xlab(" ")+theme(axis.text.x=element_text(hjust=c(.3,.6)))
mfqp1

scaredp1=sjPlot::plot_model(scaredq1lmeHVMDDsen, show.intercept = TRUE, title="",legend.title = "",dodge = .2, type="pred",terms=c("Year","Group","Gender"))+ylim(c(-.5,4.5))+theme_classic(base_size=baseFontSize)+ylab("Anxiety Symptoms")+xlab(" ") +theme(axis.text.x=element_text(hjust=c(.3,.6)))
scaredp1

```

#### Q1-MFQ - part c - Sensitivity Analysis: Trajectory of depressive symptoms before and during the pandemic for MDD participants with no inpatient/outpatient visit. 

```{r mfq-q2b, eval=TRUE, echo=FALSE, warning=FALSE} 

smqf2020N=s_mfq_with_no_in_out%>%group_by(Participant, Year) %>% dplyr::count(.)
ParticipantLessThan2=smqf2020N %>% filter(n < 2)
smfqTraj=s_mfq%>%filter(Group=="MDD" & !(Participant %in% ParticipantLessThan2$Participant)) %>% filter(Participant %in% s_mfq_with_no_in_out$Participant)

mfq2blme=lmerTest::lmer(measureName~Gender+Time*Year+(1+Time*Year|Participant), data=smfqTraj, control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
#summary(mfq2blme)
sjPlot::tab_model(mfq2blme,dv.labels= "Depressive Symptoms")
print("Slope during the pandemic: Time + Time * Year [Pandemic]: ")
a=lmerTest::contest1D(mfq2blme, c(0,0,1,0,1),confint=TRUE) #to get slope during the pandemic
print(a, digits=3)

mfqp2b=sjPlot::plot_model(mfq2blme, show.intercept = TRUE, title="", type="pred",terms=c("Time","Year","Gender"),colors=c("darkgreen","purple"), legend.title="") 
mfqp2b=mfqp2b+xlab("Months since March")+ylab("Depressive Symptoms")+xlim(c(0,12.5))+ylim(c(-2,18))+scale_x_discrete(name ="", 
                    limits=c("April","May","June","July","August","September","October","November","December","January","February"))
mfqp2b=mfqp2b+ theme_classic(base_size=16) + theme(axis.text.x = element_text(angle=90))
mfqp2b


```

#### Q1-SCARED b - Sensitivity Analysis: Trajectory of anxiety symptoms before and during the pandemic for MDD participants excluding subjects with inpatient/outpatient visits. 
```{r scared-q3b, eval=TRUE, echo=FALSE, warning=FALSE} 

sscared2020N=s_scared%>%group_by(Participant, Year) %>% dplyr::count(.)
ParticipantLessThan2=sscared2020N %>% filter(n < 2)
sscaredTraj=s_scared%>%filter(Group=="MDD" & !(Participant %in% ParticipantLessThan2$Participant))%>% filter(Participant %in% s_mfq_with_no_in_out$Participant)

a=sscaredTraj %>% group_by(Participant) %>% slice(1)

scaredq2blme=lmerTest::lmer(measureName~Gender+Time*Year+(1+Time*Year|Participant), data=sscaredTraj,control=lme4::lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
#summary(scaredq2blme)
sjPlot::tab_model(scaredq2blme,dv.labels= "Anxiety Symptoms")
print("Slope during the pandemic (Time + Time * Year [Pandemic]) ")
a=lmerTest::contest1D(scaredq2blme, c(0,0,1,0,1),confint=TRUE) #to get just MDD
print(a, digits=3)

scaredp2b=plot_model(scaredq2blme, title="", type="pred", terms=c("Time","Year", "Gender"),colors=c("darkgreen","purple"), legend.title="")+xlab("Months since March")+ylab("Anxiety Symptoms")+xlim(c(0,12.5))+ylim(c(-.5,4.5))+scale_x_discrete(name ="", limits=c("April","May","June","July","August","September","October","November","December","January","February")) 
scaredp2b=scaredp2b+ theme_classic(base_size=16) + theme(axis.text.x = element_text(angle=90))
scaredp2b

#?convergence
# fm1.all <- lme4::allFit(scaredq2blme)
# ss=summary(fm1.all)
# ss$fixef

```

### Comparision of MDD trajectory pre and during the pandemic, excluding subjects who participated in inpatient or outpatient treatment
```{r mfq-scared-sen, eval=TRUE, echo=FALSE, warning=FALSE,message=FALSE}
tab_model(mfq2blme,scaredq2blme, dv.labels =c("Depressive Symptoms","Anxiety Symptoms"),show.re.var = FALSE, string.pred=" ", file="self-mfq-scared-q1part2b-female-male.html")

```

```{r mfq-scared-q3b, eval=TRUE, echo=FALSE, warning=FALSE} 
ggsave("self-mfq-scared-plots-female-male-2subplots-without-in-outpatient-v2.png", arrangeGrob(mfqp2b, scaredp2b, nrow=1,widths=c(20,20), heights=c(15)), width=15, height=5)
```

### Histograms of measures
```{r mfq-scared-crisis, eval=TRUE, echo=FALSE, warning=FALSE,message=FALSE}

#**************** Histograms of MFQ measures for pre and during pandemic for HV -------------------------------------
before=s_mfq %>% filter(Group=="HV" & Year=="Pre-Pandemic") 
after=s_mfq %>%  filter(Group=="HV" & Year=="Pandemic") 
beforeCountHV=before %>% group_by(Participant) %>% dplyr::count()
print("----Summary of MFQs for HVs, Pre-Pandemic")
print(summary(beforeCountHV$n))
afterCountHV=after %>% group_by(Participant) %>% dplyr::count()
print("----Summary of MFQs for HVs, During Pandemic")
print(summary(afterCountHV$n))
qplot(beforeCountHV$n, geom="histogram", fill=I("lightblue"),col=I("lightblue"),alpha=I(.5),ylab ="Number of Participants",xlab="Number of Depressive Symptoms Ratings",main="HV Pre-Pandemic",show.legend = FALSE, xlim=c(0,30), ylim=c(0,60))+theme_classic(base_size = 18)
#ggsave("HV-pre.png", height=5, width=6)
qplot(afterCountHV$n, geom="histogram", fill=I("lightblue"),col=I("lightblue"),alpha=I(.5),ylab ="Number of Participants",xlab="Number of Depressive Symptoms Ratings",main="HV During Pandemic",show.legend = FALSE, xlim=c(0,30), ylim=c(0,60))+theme_classic(base_size = 18)
#ggsave("HV-during.png", height=5, width=6)

#**************** Histograms of MFQ measures for pre and during pandemic for MDD --------------------------------------
before=s_mfq %>% filter(Group=="MDD" & Year=="Pre-Pandemic") 
after=s_mfq %>%  filter(Group=="MDD" & Year=="Pandemic") 
beforeCountMDD=before %>% group_by(Participant) %>% dplyr::count()
print("----Summary of MFQs for MDD Group, Pre-Pandemic")
print(summary(beforeCountMDD$n))
afterCountMDD=after %>% group_by(Participant) %>% dplyr::count()
print("----Summary of MFQs for MDD Group, During Pandemic")
print(summary(afterCountMDD$n))
qplot(beforeCountMDD$n, geom="histogram", fill="red",col=I("red"),alpha=I(.5),ylab ="Number of Participants",xlab="Number of Depressive Symptoms Ratings",main="MDD Pre-Pandemic",show.legend = FALSE, xlim=c(0,30), ylim=c(0,60))+theme_classic(base_size = 18)
#ggsave("MDD-pre.png", height=5, width=6)
qplot(afterCountMDD$n, geom="histogram", fill="red",col=I("red"),alpha=I(.5),ylab ="Number of Participants",xlab="Number of Depressive Symptoms Ratings",main="MDD During Pandemic",show.legend = FALSE, xlim=c(0,30), ylim=c(0,60))+theme_classic(base_size = 18)
#ggsave("MDD-during.png", height=5, width=6)

#**************** Histograms of CRISIS for HV and MDD --------------------------------------------------
behavioralData2=behavioralData %>% filter(!is.na(s_crisis_date)) %>% group_by(Participant,Group) %>% dplyr::count()
behavioralData2HV= behavioralData2%>%filter(Group=="HV")
behavioralData2MDD=behavioralData2%>%filter(Group=="MDD")
print("----Summary of CRISIS for HVs")
summary(behavioralData2HV$n)
print("----Summary of CRISIS for HVs")
summary(behavioralData2MDD$n)
behavioralData2Summary=rbind(summary(behavioralData2HV$n),summary(behavioralData2MDD$n))
rownames(behavioralData2Summary)=c("HV","MDD")
ggplot(aes(n),data=behavioralData2HV)+geom_bar(fill="lightblue")+xlab("Number of CRISIS ")+ylab("Number of Participants")+ylim(c(0,23))+theme_classic(base_size = 20)+ggtitle("HV During Pandemic")
#ggsave("HV-crisis.png", height=5, width=6)
ggplot(aes(n),data=behavioralData2MDD)+geom_bar(fill="indianred1")+xlab("Number of CRISIS ")+ylab("Number of Participants")+ylim(c(0,23))+theme_classic(base_size = 20)+ggtitle("MDD During Pandemic")
#ggsave("MDD-crisis.png", height=5, width=6)


```
